### 2025-02-06 paper/sections/other/constraints.qmd
uhhh

```{julia}
obj = EnergyDifferentialObjective(lambda=[1.0,0.1,0.0])
# obj = VanillaObjective()
generator = GenericGenerator()
opt_state = Flux.setup(Descent(), model)
```

@@

model, logs = counterfactual_training(
    obj,
    model,
    generator,
    train_set,
    opt_state;
    val_set = val_set,
    nepochs = 50,
    mutability = Symbol.(constraints)
)
```

>>>>

```{julia}
using CounterfactualExplanations.Convergence
obj = EnergyDifferentialObjective(lambda=[1.0,0.1,0.0])
# obj = VanillaObjective()
generator = GenericGenerator()
opt_state = Flux.setup(Descent(), model)
conv = MaxIterConvergence()
```

```{julia}
function plot_db(model, x)
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    plt = Plots.scatter(ce_data)
    yhat = [argmax(y) for y in eachcol(model(x))]
    Plots.scatter!(x[1,:], x[2,:], label="Counterfactuals", ms=15, shape=:star, color=yhat)
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")
    display(plt)
end
```

@@

model, logs = counterfactual_training(
    obj,
    model,
    generator,
    train_set,
    opt_state;
    val_set = val_set,
    nepochs = 20,
    mutability = Symbol.(constraints),
    callback = plot_db,
    nce=50,
    convergence=conv, 
)
```
